Parsing Postfix log files

### 2008-04-30 doc/logparser-other-parsers-review.tex
Improved other parsers introduction. Sawmill tested. YAALA tested.

@@

@@

YAALA provides a mini-language based on \SQL{} that is used when generating
reports; sample reports can be seen at~\cite{yaala-samples}.  Example
query: \newline \tab{} \texttt{requests BY file WHERE host =\~{} Google}
\newline The mini-language is quite limited and cannot be used to extract
data for external use, merely to create reports.

In summary YAALA provides a Postfix parser which only handles the most
common Postfix log lines, provides reasonably flexible report generation
from the limited data extracted, but has no facilities to extract data for
use in other tools.

>>>>

    \item Most of the parsers silently ignore log lines they cannot handle,
        whereas \parsername{} complains loudly about every single line it
        fails to parse.  The exception is AWStats, which outputs the
        percentage of input lines it was unable to parse, but does not
        output the lines themselves.

    \item A minor difference is that most parsers don't handle compressed
        files; both \parsername{} and Splunk handle them transparently,
        without user intervention; Sawmill and Lire can be configured to
        support compressed files, but Sawmill exhibits a dramatic slow down
        when thus configured.  Although this is a minor difference, support
        for reading compressed log files is quite helpful, as it
        dramatically reduces the disk space required to store old logs.

@@

When tested with the \numberOFlogFILES{} test log files it performed
adequately, though the rate it processed log files at did slow down
noticeably as it progressed.  Sawmill supports reading compressed log files
but it exhibits a dramatic slow down when doing so: it took six hours to
parse the first half of the log files; twelve hours to parse the next
third; after twenty four hours parsing the remaining sixth it crashed due
to lack of disk space.  On the second parsing attempt the log files were
uncompressed beforehand and parsing took eight hours.

Sawmill's web interface supports searching on any combination of the fields
it extracts, but the interface is neither as simple to use nor as
informative as the interface provided by Splunk.  The administrative
interface is very easy to use --- it took only five minutes to start
parsing a directory of log files.

@@

YAALA provides a mini-language based on \SQL{} that is used when generating
reports; sample reports can be seen at~\cite{yaala-samples}.  Example
query: \newline \tab{} \texttt{requests BY file WHERE host =\~{} Google}
\newline The mini-language is quite limited and cannot be used to extract
data for external use, merely to create reports.  Only data selected by the
query will be saved in the data store; other data will be discarded, and
removed from the data store if already present.

Testing YAALA was unsuccessful because all the select clauses tried
produced a similar error message:
\newline\tab{}\texttt{lib/Yaala/Data/Core.pm: Unavailable aggregation
requested:} \newline\tab{}\texttt{``bytes''. Returning 0.} \newline  The
underlying reason for this is that YAALA only parsed 408 log lines of
360632 log lines (0.11\%) in the first log file.

In summary YAALA provides a Postfix parser which only attempts to parse the
most common Postfix log lines (but fails miserably), provides reasonably
flexible report generation from the limited data extracted, but has no
facilities to extract data for use in other tools.
